preciseTAD: A machine learning framework for precise TAD boundary prediction at base-level resolution

### 2020-08-30 Manuscript/manuscript.Rmd
added to supp fig5; editted legend

**Supplementary Figure 5.** Profile plots comparing the signal strength of top TFBS around flanked (A) Arrowhead called TAD boundaries (blue) and *preciseTAD*-predicted TAD boundaries (green), and (B) around Peakachu loop boundaries (red) and preciseTAD predicted loop boundaries (green) on K562.

>>>>

**Supplementary Figure 5.** Profile plots comparing the signal strength of top TFBS around flanked (A) Arrowhead called TAD boundaries (blue) and *preciseTAD*-predicted TAD boundaries (green), (B) Peakachu chromatin loop boundaries (red) and preciseTAD predicted loop boundaries (green) on K562, (C) Arrowhead called TAD boundaries (blue), Peakachu chromatin loop boundaries (red), and SpectralTAD called TAD boundaries (green) on GM12878 and (D) on K562.
